# Introduction to simple plots and basic statistics in R

# A sample dataset

## Let's use `data.frame` to build a simple table of data to work with.

Usually you'd be loading data from an external file, but we'll use this example to demonstrate the `rep` function:

``` {r}
rep(c("a","b"), times = 3)
rep(c("a","b"), each = 2)
rep(c("a","b"), times = 3, each = 3)
````

## Clotting time dataset 

We'll have 12 observations, the first 6 with "drug1" the second 6 with "drug2"

``` {r}
clotData <- data.frame(
                drugType = rep( c("drug1", "drug2"), each = 6 ),
                clotTime = c( 8.8, 8.4, 7.9, 8.7, 9.1, 9.6, 9.9, 9.0, 11.1, 
                              9.6, 8.7, 10.4)
              )

clotData
````

# Summary statistics

## General summary

The `summary` function provides a simple way to get a standard set statistics:

``` {r}
summary(clotData)
````

## Summary by factor

What if we wanted individual summaries of the data for each drug type?

``` {r}
by(clotData, INDICES = clotData$drugType, FUN = summary)
````

What happened there?

## Aggregate by a factor

How can we make a new table with just average clot times for each drug?

``` {r}
aggregate(clotData$clotTime, 
          by  = list(Drug=clotData$drugType), 
          FUN = mean)
````

What happened there?

# Simple plots

## The plot function is magic!

``` {r}
plot(clotData)
````

This is a [box plot](http://en.wikipedia.org/wiki/Box_plot).

## Simple x,y plot

``` {r}
plot(c(1,2,3,4), c(2,3,4,5))
````

## Simple f(x) plot

``` {r}
plot( function(x) { x * 4} )
````

## Simple f(x) plot

``` {r}
plot( function(x) { x ^ 2} )
````

## Let's plot a normal distribution in blue

``` {r}
x <- seq(-4, 4, length = 200)
y <- dnorm(x, mean = 0, sd = 1)
plot( x, y, col = "blue")
````

## Two plots on one graph
``` {r}
x <- seq(-4, 4, length = 200)
y1 <- dnorm(x, mean = 0, sd = 1)
y2 <- dnorm(x, mean = 1, sd = 1)
plot( x, y1, type = "l", col = "blue" )
lines( x, y2, col = "red" )
````

# A simple t-test

## Let's look at those box plots again:

``` {r}
plot(clotData)
````

Are the sample means different?

## The t-test {stats}

``` {r}
help(t.test)
help.search("t.test")
````

## The formula expression

``` {r}
library(stats)
t.test(clotData$clotTime ~ clotData$drugType)
````

## The data.frame short cut

``` {r}
t.test(clotTime ~ drugType, data = clotdata)
````
